### 2021-03-05 treatise-context/1_introduction.tex
Rev criticize to Bajwa et al

Our work is also an improvement to Bajwa et.\ al.\ \cite [BHS10].
First, their method takes many time slices, but, since we consider a time independent channel matrix, a few time slices suffice.
Second, for mm waves, the channel might have a short response, requiring us to send the training signals in a short interval of time, which may not be practical.
Third, with the further constraint of hybrid beamforming, it is not clear whether their guarantee theorem for recovery is still valid.
Fourth, generating random sequences can lead to high complexity \cite [LGL16].

>>>>

Our work is also an improvement to Bajwa et.\ al.\ \cite [BHS10].
First, their method takes many time slices, but, since we consider a time independent channel matrix, a few time slices suffice.
Second, with the further constraint of hybrid beamforming, it is not clear whether their guarantee theorem for recovery is still valid.
Third, generating random sequences can lead to high complexity \cite [LGL16].

### 2021-03-05 treatise-pdflatex/1_introduction.tex
Rev criticize to Bajwa et al

Our work is also an improvement to Bajwa et.\ al.\ \cite {BHS10}.
First, their method takes many time slices, but, since we consider a time independent channel matrix, a few time slices suffice.
Second, for mm waves, the channel might have a short response, requiring us to send the training signals in a short interval of time, which may not be practical.
Third, with the further constraint of hybrid beamforming, it is not clear whether their guarantee theorem for recovery is still valid.
Fourth, generating random sequences can lead to high complexity \cite {LGL16}.

>>>>

Our work is also an improvement to Bajwa et.\ al.\ \cite {BHS10}.
First, their method takes many time slices, but, since we consider a time independent channel matrix, a few time slices suffice.
Second, with the further constraint of hybrid beamforming, it is not clear whether their guarantee theorem for recovery is still valid.
Third, generating random sequences can lead to high complexity \cite {LGL16}.
